Image Processing for Discovering\\ the Rules of Video Games

### 2018-04-18 proposal/paper.tex
added image support and images folder

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\section{Image Processing}
The image processing algorithm gets the image from the lua bridge and applies the following operations to identify object in an image and pass them on to the Q-Learning/NEAT algorithms.

@@

\textbf{Change Resolution:}
The resolution is being reduced to reduce the information density with the thought that only the most prominent features will be available afterwards. This works well for finding characters and objects in the image but most of the time any text based information like the score is lost.

\textbf{Convert to Grayscale:}
This steps helps improve the speed of the algorithm since the algorithm has to only deal with 8-bits of color instead of 24-bits. The grayscale conversion function can be provided with weight parameters for red, green and blue (RGB). This allows the highlighting of certain objects of interest.

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\graphicspath{ {images/} }

@@

\section{Image Processing}
The image processing algorithm gets the image from the lua bridge and applies the following operations to identify object in an image and pass them on to the Q-Learning/NEAT algorithms.\\ \\
\includegraphics[scale=0.45]{frame626}

@@

\textbf{Change Resolution:}
The resolution is being reduced to reduce the information density with the thought that only the most prominent features will be available afterwards. This works well for finding characters and objects in the image but most of the time any text based information like the score is lost.\\ \\
\includegraphics[scale=3]{6xdown}

\textbf{Convert to Grayscale:}
This steps helps improve the speed of the algorithm since the algorithm has to only deal with 8-bits of color instead of 24-bits. The grayscale conversion function can be provided with weight parameters for red, green and blue (RGB). This allows the highlighting of certain objects of interest.\\ \\
\includegraphics[scale=3]{gray}
